The SMT Competition 2015--2018

### 2019-03-14 2018/report/SMT-COMP.tex
Add VBS cactus plots.

\usepackage{pifont}
\usepackage{multirow}
\usepackage{tikz}

@@

>>>>

%\usepackage{showframe}   % debug

\usepackage{pifont}
\usepackage{multirow}
\usepackage{tikz}
\usepackage{subcaption}

@@

\begin{figure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2014-2015.pdf}}
    \caption{2014 vs.~2015}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2015-2016.pdf}}
    \caption{2015 vs.~2016}
  \end{subfigure}
  \\[4ex]
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2016-2017.pdf}}
    \caption{2016 vs.~2017}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2017-2018.pdf}}
    \caption{2017 vs.~2018}
  \end{subfigure}
  \caption{Virtual Best Solver (VBS) on common benchmarks of all
  logics in the Main Track.}
\end{figure}
